### 2014-04-19 article.tex
Make skeleton structure for article. Add more references.

@@

\section{Introduction}
According to \textcite{cea2012bathymetric} the effects of bathymatric uncertainty are well understood. However, it has been shown that a higher albedo leads to cooling.

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/foweyROI}
    \caption{Composite satellite image of the Fowey Estuary}
    \label{fig:fowey_estuary}
\end{figure}

\section{Methods}

\section{Results}
Results to go here. As can be seen in Figure~\ref{fig:rising_tide}.

@@

@@

\section{Methods}
Methods

>>>>

% Third person throughout.

@@

\section{Introduction}

What is being modelled. Dredging.

\subsection{Area of study}

Does it need its own subsection?

\begin{figure}[hbp]
    \centering
    \includegraphics[width=10cm]{geogg101_screenshots/practical1/fowey_estuary_map}
    \caption{Map of the Fowey Estuary. Taken from \textcite{friend2006sediment}.}
    \label{fig:fowey_estuary}
\end{figure}

\section{Methodology}

\subsection{Model}

Two-dimensional depth averaged model named RMA-2 \parencite{king1990program}. It was developed within the SMS modelling package, which was used to create the mesh and control the model runs.

\subsection{Model setup}

Mesh. Boundary conditions. Bathymetry. Other?

\subsection{Calibration}
Following \textcite{piedra2007residual, sousa2007hydrodynamic} the  Manning number was varied to achieve the best fit between the model and the observations. talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}

\subsection{Dredging scenario}

\section{Results and discussion}
Results to go here. As can be seen in Figure~\ref{fig:rising_tide}.

@@

\section{Conclusions}
Is this section necessary?

@@

\section{Methodology}
Methods
